Template for GTEx example on cluster

### 2017-10-06 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

```{r}
gt10 = readRDS('../data/GTExdata/SFAres/sfaTK_10m.rds')
mu = sapply(seq(1:44),function(x){gt10$mu[[x]]})
par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
barplot(mu,main = "mean vector")
for(k in 1:10){
  barplot(gt10$LF$L[,k],main = paste("factor",k))
}
```

>>>>

```{r}
load("../data/GTExdata/gtexEQTL_zscore.rds")
gt10 = readRDS('../data/GTExdata/SFAres/sfaTK_10m.rds')
ssy = sum(zscore^2)
pve = sapply(seq(1:10),function(x){sum((gt10$LF$L[,x] %*% t(gt10$LF$F[x,]))^2)})
pve = pve/ssy

mu = sapply(seq(1:44),function(x){gt10$mu[[x]]})
par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
barplot(mu,main = "mean vector")
for(k in 1:10){
  barplot(gt10$LF$L[,k],main = paste("factor",k,"pve",round(pve[k],3)))
}
```
